Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs with the Uniform Kernel

### 2016-02-29 main_paper.tex
Make additional changes to theoretical results
This commit tightens some of the language around Algorithm and Theorem 1 and also
makes some small notation adjustments in the text and proof.

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{gather*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau = h^{2}\Bs(h)\{1+o_{p}(1)\}
  \intertext{with}
  \Bs(h)=\tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h)
\end{gather*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend
on the data, kernel, and bandwidth. The plug-in bias-corrected estimator then
requires estimates for the second derivatives of the conditional mean from above
and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that
these derivatives can be estimated by fitting a second order local polynomial,
i.e. one order higher than the polynomial used to obtain $\hat{\tau}$, using a
(potentially) different pilot bandwidth $b$. Their procedure gives the
bias-corrected estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2} \hat{\Bs}(h,b)
  \intertext{with}
  \hat{\Bs}(h,b) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h).
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
  \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_-(h) &= \{i : -h < X_{i} < 0\}, &
    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in
  $I_-(h)$ and $I_+(h)$ respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
    the observations in $I_-(b)$ and $I_+(b)$:
    \begin{align*}
      \hat g_-(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
      &\hat g_+(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
    \end{align*}
    with
    \begin{align*}
      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_1$ times to produce a sequence of
    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}(h)^*$. For the
    $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M^-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_i^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align*}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align*}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align*}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align*}
    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
    \end{equation*}
  \end{enumerate}
\end{algorithm}
The distribution of $\Delta^{*}$ depends on $B_{1}$ and we could
incorporate that dependency into our notation by writing $\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
literature and assume that $B_{1}$ is large enough that it can be ignored and define $\Delta^* = \plim_{B_{1} \to \infty} \Delta^*_{B_{1}}$

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{align*}
  \frac{(\hat\tau(h,b) - \Delta^{*}(h,b) - \tau)}{ V^{1/2}(h, b)} \to^{d} N(0,1)
\end{align*}
\end{theorem}

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I_-$, $I_+$, $M_-$, and $M_+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_{i} : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{i}^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align*}
        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align*}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align*}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M_-(b)}^{*-},X_{M_-(b)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M_+(b)}^{*+},X_{M_+(b)}^{*+}),
      \end{equation*}
      using the same bandwidths $h$ and $b$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

\appendix
\section{Mathematical appendix}
\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
    \E^* \hat\tau^{*}_h - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf(h)/2
      - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
  &= \hat\tau_h - \E\hat\tau_h
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  &= \hat\tau_h - \E\hat\tau_h
   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \notag \\
  \label{eq:2}
  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:2} to get
\begin{align*}
  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*_h - \E^*\hat\tau^*_h
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega^{+}(b)' \epb_{+}^{*} - \Omega^{-}(b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b) - \Omega_{2i}^{+}(b)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m^+_i} / h) \1\{h > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &= (0\quad 0 \quad h^2)
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega^+(b)$ after making the obvious
substitutions of ``$-$'' for ``$+$.''

Given~\eqref{eq:2}, it suffices to prove that
\begin{gather}
  \label{eq:3}
  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
    V^{-1/2}(h)\Omega^{+}(b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:4}
  \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
    V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
    & \text{with probability\ } 1/M_{b}^+ \\
    \vdots \\
    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
    & \text{with probability\ } 1/M_{b}^+,
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}

>>>>

CCT solve this problem by deriving the analytical form of the first-order bias
and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
asymptotic behavior of the bandwidth, which we will specify in
Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
form
\begin{equation*}
  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
  (1+o_{p}(1))
\end{equation*}
where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
these terms are given in the Mathematical Appendix as Equations~\eqref{eq:3}
and~\eqref{eq:4}. The plug-in bias-corrected estimator then requires estimates
for the second derivatives of the conditional mean from above and below the
cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
can be estimated by fitting a second order local polynomial, i.e. one order
higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
different pilot bandwidth $b$. Their procedure gives the bias-corrected
estimator
\begin{gather*}
  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
\end{gather*}
The variance introduced by the bias-correction term does not vanish, so the
naive confidence interval needs not only to be re-centered to correct the bias,
but also rescaled to allow for the additional variability introduced by the bias
correction, resulting in the following asymptotic approximation:
\begin{equation*}
  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
  \to^d N(0,1)
\end{equation*}
with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
generated by the bias-correction term. This new approximation can be used
instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
and CCT provide simulation evidence that their intervals perform well in finite
samples.

@@

\begin{algorithm}[Bias estimation]\label{Alg1}
  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
  \begin{align*}
    I_-(h) &= \{i : -h < X_{i} < 0\}, &
    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
  \end{align*}
  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
  $I_-(h)$ and $I_+(h)$ respectively.
  \begin{enumerate}
  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
    the observations in $I_-(b)$ and $I_+(b)$:
    \begin{align*}
      \hat g_-(x)
      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
      &\hat g_+(x)
      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
    \end{align*}
    with
    \begin{align*}
      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
    \end{align*}
    Calculate the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_{i} - \hat g_+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_1$ times to produce a sequence of
    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
    $k$th estimate:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
      construct
      \begin{align*}
        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
      \end{align*}
    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
      local linear model on the bootstrap data set:\footnote{%
        Note that the indices of summation are chosen to correspond to the
        indices of the variables generated in the previous step.} %
      \begin{align*}
        \hat\mu_-^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2 \\
        \hat\mu_+^*(h)
        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
          (Y_i^* - \mu - \beta X_i^*)^2.
      \end{align*}
    \item Save $\hat\mu_+^*(h) - \hat\mu_-^*(h)$ as $\hat\tau^*_k$.
    \end{enumerate}
  \item Estimate the bias as
    \begin{equation*}
      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
      \big[\hat g_+(0) - \hat g_-(0)\big].
    \end{equation*}
  \end{enumerate}
\end{algorithm}

@@

\begin{theorem}\label{T1}
  Under Assumptions~\ref{A1} and~\ref{A2},
\begin{equation}
  \label{eq:2}
  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V(h, b)^{1/2}}
  \to^{d} N(0,1)
\end{equation}
\end{theorem}

Note that the variance component of~\eqref{eq:2} is the same value used by CCT
and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our
bias-corrected estimator has the same asymptotic distribution as CCT's. This
equivalence should be unsurprising; both estimators use a 2nd order polynomial
to directly estimate the bias of the local linear model, so they should behave
very similarly.

@@

\begin{algorithm}[Confidence intervals]\label{Alg2}
  Define $I_-$, $I_+$, $M_-$, and $M_+$ as in Algorithm~\ref{Alg1}.
  \begin{enumerate}
  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
    Equation --- and define the residuals
    \begin{equation*}
      \hat\varepsilon_{i} =
      \begin{cases}
        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
      \end{cases}
    \end{equation*}
  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
    \begin{enumerate}
    \item Draw an i.i.d. sample of size $M_-(b)$ from
      $\{\hat\varepsilon_{i} : i \in I_-(b)\}$ and one of size $M_+(b)$ from
      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{i}^{*-}$ and
      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
      \begin{align*}
        Y_{-,i}^* &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
        Y_{+,i}^* &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
      \end{align*}
    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
      \begin{align*}
        \hat\mu_-^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_-(h)} (Y_{-,i}^* -
          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
        \hat\mu_+^*
        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
          \sum_{i = 1}^{M_+(h)} (Y_{+,i}^* -
          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
      \end{align*}
    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
      \begin{equation*}
        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M_-(b)}^{*-},X_{M_-(b)}^{*-}),
        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M_+(b)}^{*+},X_{M_+(b)}^{*+}),
      \end{equation*}
      using the same bandwidths $h$ and $b$ that are used in the rest of
      this algorithm but reestimating all of the local polynomials on the
      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
      by Algorithm~\ref{Alg1}.
    \item Save the bias-corrected estimator
      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
    \end{enumerate}
  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
  \end{enumerate}
\end{algorithm}

@@

\appendix
\section{Mathematical appendix}

Define the following additional notation:
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align}
  \label{eq:3}
  \Bf_+(h)
  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \label{eq:4}
  \Bf_-(h)
  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align}

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
The design of the bootstrap ensures that
\begin{align*}
  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely, implying that
\begin{equation*}
    \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
      - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
Combining this result with CCT's Lemma A1, gives
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:5}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:5} to get
\begin{align*}
  \hat\tau(h)^* - &\Delta_h^{**} - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega^{+}(b)' \epb_{+}^{*} - \Omega^{-}(b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
$\Omega_{1i}^{+}(b) - \Omega_{2i}^{+}(b)$, which are defined as
\begin{align*}
  \Omega_{1i}^{+}(b) &=
  (1\quad 0)
  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m^+_i} / h) \1\{h > X_{m_i} \geq 0\}
\intertext{and}
  \Omega_{2i}^{+}(b) &= (0\quad 0 \quad h^2)
  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m^+_i} / b).
\end{align*}
Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
$\epb_{-}^{*}$ and $\Omega^-(b)$ have the same definitions as
$\epb_{+}^{*}$ and $\Omega^+(b)$ after making the obvious
substitutions of ``$-$'' for ``$+$.''

Given~\eqref{eq:5}, it suffices to prove that
\begin{gather}
  \label{eq:6}
  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
    V^{-1/2}(h)\Omega^{+}(b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:7}
  \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
    V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}) \to^p 0
\end{gather}
with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
element of which is distributed as
\[
  \varepsilon_{i,+} =^d
  \begin{cases}
    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
    & \text{with probability\ } 1/M_{b}^+ \\
    \vdots \\
    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
    & \text{with probability\ } 1/M_{b}^+,
  \end{cases}
\]
$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
  is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}
